Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-18 bdcloud_paper/latex/paper.tex
Updated cluster analysis for 10,000 customers

Secondly, we profiled our customers' purchasing habits to optimize the advertising campaign's effectivness by customizing the advertized products for each customer.  For each customer, we generated a feature vector by computing the frequency with which they would purchase the same brand or flavor from one transaction to the next.  We clustered the customers' feature vectors using the KMean algorithm with a range of cluster counts. The clustering identified 16 centers, determined by the convergence of the error.

@@

\subsection{Customer Locations}

\subsection{Customer Purchasing Profiles}

%\begin{figure*}[!t]
%  \centerline{\subfloat[Case I}{\includegraphics[width=2.5in]{figures/cluster_error.eps}
%    \label{fig:cluster_error}}
%  \hfil
%  \subfloat[Case II]{\includegraphics[width=2.5in]{figures/cluster_analysis.eps}
%    \label{fig:cluster_analysis}}}
%  \caption{Clustering of Brand and Flavor Preferences}
%  \label{fig:clustering}
%\end{figure*}

* stores -- distance, one or multiple stores?
* brand loyalty

\section{Scaling of Data Size and Run Time}
BigPetStore aims to scale from a local desktop to a large cluster. As a result, we benchmarked the generation of data on a laptop with a 2 GHz Intel Core i7 CPU, 8 GB of RAM, and a 256 GB SSD using the Python implementation with a single thread. Using the test setup, between 1,500 and 2,000 transactions can be generated per second (Table~\ref{tab:benchmarks}).

>>>>

Secondly, we profiled our customers' purchasing habits to optimize the advertising campaign's effectivness by customizing the advertized products for each customer.  For each customer, we generated a feature vector by computing the frequency with which they would purchase the same brand or flavor from one transaction to the next.  We clustered the customers' feature vectors using the KMean algorithm with a range of cluster counts. Twenty clusters converged the error.

@@

\section{Scaling of Data Size and Run Time}
BigPetStore aims to scale from a local desktop to a large cluster. As a result, we benchmarked the generation of data on a laptop with a 2 GHz Intel Core i7 CPU, 8 GB of RAM, and a 256 GB SSD using the Python implementation with a single thread. Using the test setup, between 1,500 and 2,000 transactions can be generated per second (Table~\ref{tab:benchmarks}). As the customers' transaction simulations are independent of one another, the transaction generation can easily be parallelized so that 1,500-2,000 transactions can be generated per thread per second.
